\LARGE \bf Reactive Trajectory Planning and Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-04-14 root.tex
more reviewer comment changes

When a pedestrian is detected, the nominal distance needed to stop, $\Delta s_{RSTOP}$, must be computed given the vehicle's current location, speed, and forward acceleration.
??????????? The procedure for doing this is the same as the procedure for planning the RSTOP trajectory with fewer steps, since the planning algorithm is quite efficient. ?????????? not clear

@@

This procedure is repeated when the nearest pedestrian location changes by a value more than some static buffer $\Delta s_{replan} < \Delta s_{buf}$ compared to the location for which the current RSTOP planned.
$\Delta s_{replan}$ value is typically set to 1 meter.
Normal operation is resumed when the distance between the vehicle and the closest detected pedestrian satisfies $s_{ped} - s_{veh} > \Delta s_{resume} + \Delta s_{RSTOP}$. The static resume buffer should be set such that $\Delta s_{resume} > \Delta s_{buf} + \Delta s_{replan}$.
These quantities are depicted graphically in Fig. \ref{fig:react}.

@@

In this section, we describe our approach to fitting appropriate jerk profiles to complex sub-paths. 
We first break each sub-path into segments with a simple shape.
Then each segment can be compared to a library of possible jerk profiles to find a good match.
Each segment is defined by the vector $\mathbf{b}  = [v_i, a_i, L, v_m, v_f]$, being initial speed, initial acceleration, the total distance, speed limit, and the final speed, respectively.
Additionally, the desired positive and negative acceleration $\mathbf{a}_m = [a^+_m , a^-_m]$ and the desired positive and negative jerk $\mathbf{j}_m = [j^+_m , j^-_m]$ must be defined for each segment.
A sub-path is then a set of $N$ segments, each of which is defined by a set of parameters $\mathbf{b}_{k}$, $\mathbf{a}_{m,k}$, and $\mathbf{j}_{m,k}$ where $k = 1, ..., N$ and can be solved individually in sequence.

@@

The {\it Ceiling Calculation} is a minimax problem.
Each of the 9 scalars in $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ is a minimum of several maxima computed from an arbitrary set of constraints.
For instance, acceleration constraints may include a set of limits derived from friction coefficients at every point along the sub-path.

% How we actually did this.
For the purposes of developing a simple example application, two constraints will be used for $v_{m}$: legal speed limit $SL$ and lateral acceleration limit $a_{B,y}^{max}$. 
Lateral acceleration constraints are translated into longitudinal speed constraints using the approximation 
%\textbf{ RG: using centrifugal  force relationship ????} 
$v_{m,w}(a_{B,y}) = \sqrt{a_{B,y}^{max}/\kappa_{w}}$ for $w = 1, ..., W$, where $W$ is the number of waypoints in the sub-path.
The value $\kappa_{k_P}$ denotes the path curvature at each point.
For each sub-path point, the value $v_{m,w}(a_{B,y}^{max})$ denotes the speed necessary to obtain the limit lateral acceleration, denoted by $a^{max}_{B,y}$.

>>>>

When a pedestrian is detected, the nominal distance needed to stop, $\Delta s_{RSTOP}$, must be computed given the vehicle's current location, speed, and forward acceleration.
This serves as a dynamic buffer between the pedestrian and the vehicle.
In order to calculate $\Delta s_{RSTOP}$, a hypothetical trajectory plan is created (but not implemented).
A 3-phase profile using the vehicle's current state as initial conditions and $v_f = 0$ is created, and the resultant distance then becomes the nominal required stopping distance.

@@

This procedure is repeated when the nearest pedestrian location changes by a value more than some static buffer $\Delta s_{replan} < \Delta s_{buf}$ compared to the location for which the current RSTOP planned.
$\Delta s_{replan}$ value is typically set to 1 meter.
Normal operation is resumed when the distance between the vehicle and the closest detected pedestrian satisfies $s_{ped} - s_{veh} > \Delta s_{resume} + \Delta s_{RSTOP}$. The static resume buffer should be set such that $\Delta s_{resume} > \Delta s_{buf} + \Delta s_{replan}$.
These quantities are depicted graphically in Fig. \ref{fig:react}.
Nominal parameter values are: $\Delta s_{buf} = 8.5 m$, $\Delta s_{replan} = 1.0 m$, $\Delta s_{resume} = 12.5 m$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this section, we describe our approach to fitting appropriate jerk profiles to complex sub-paths. 
We first break each sub-path into segments with a simple shape.
Then each segment can be compared to a library of possible jerk profiles to find a good match.
Each segment is defined by the vector $\mathbf{b}  = [v_i, a_i, L, v_m, v_f]$, being initial speed, initial acceleration, the total distance, speed limit, and the final speed, respectively.
Additionally, the desired positive and negative acceleration $\mathbf{a}_m = [a^+_m , a^-_m]$ and the desired positive and negative jerk $\mathbf{j}_m = [j^+_m , j^-_m]$ must be defined for each segment.
For this work, they are set constant for all segments.
However, this functionality enables behaviors such as more sedate driving in a school zone or when traversing small areas with lower friction coefficients, such as patches of ice or gravel detected via camera.
A sub-path is then a set of $N$ segments, each of which is defined by a set of parameters $\mathbf{b}_{k}$, $\mathbf{a}_{m,k}$, and $\mathbf{j}_{m,k}$ where $k = 1, ..., N$ and can be solved individually in sequence.

@@

The {\it Ceiling Calculation} is a minimax problem.
Each of the 9 scalars in $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ is a minimum of several maxima computed from an arbitrary set of constraints.
For instance, acceleration constraints may include a set of limits derived from friction coefficients at every point along the sub-path.
Any number of constraint sets may be used to compute the ceiling.

% How we actually did this.
For the purposes of developing a simple example application, two constraints will be used for $v_{m}$: legal speed limit $SL$ and lateral acceleration limit $a_{B,y}^{max}$. 
Lateral acceleration constraints are translated into longitudinal speed constraints using the approximation 
%\textbf{ RG: using centrifugal  force relationship ????} 
$v_{m,w}(a_{B,y}) = \sqrt{ | a_{B,y}^{max} / \kappa_{w} | }$ for $w = 1, ..., W$, where $W$ is the number of waypoints in the sub-path.
The value $\kappa_{k_P}$ denotes the path curvature at each point.
For each sub-path point, the value $v_{m,w}(a_{B,y}^{max})$ denotes the speed necessary to obtain the limit lateral acceleration, denoted by $a^{max}_{B,y}$.
